---
title: "Using neural network to predict close price of A Index"
author: "ZhouDan"
date: "2016年5月31日"
output:
  pdf_document:
    latex_engine: xelatex
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Neural Network

Here,I'm trying to represent my RPROP neural network.
If you can come up with my steps,I'm sure you can understand what I do.

##First,let's set the working directory.
And then read the raw data into R.

```{r one}
getwd()
setwd('/Users/zhoudan/Neural Network')
A_index<-data.frame(read.csv("A_index.csv",header=T))
head(A_index)
A_index$X<-NULL
A_index$index<-NULL
head(A_index)
```

## Data preprocession

Check if exist NA and finish data cleaning

```{r two}
apply(A_index, 2, function(x) sum(is.na(x)))
dates<-as.Date(A_index[,1])
A_index$date<-NULL
head(A_index)
nrow(A_index)
```

Split the dataset into train dataset and test dataset and normalized the data.

```{r three}
train<-A_index[c(0:500),]
test<-A_index[c(501:623),]
scaled<-as.data.frame(scale(A_index))
train_<-scaled[c(0:500),]
test_<-scaled[c(501:623),]
head(train_)
head(test_)

```

##Correlation analysis

```{r}
cor(A_index)
```

## Building the model
Library neuralnet package and try to build the neural network model

```{r four}
library(neuralnet)
n<-names(train_)
f <- as.formula(paste("close ~", paste(n[!n %in% "close"], collapse = " + ")))
nn_1<-neuralnet(f,data=train_,hidden=2,linear.output=TRUE)
nn_1
par(mfrow=c(1,1))
plot.nn(nn_1)
nn_2<-neuralnet(f,data=train_,hidden=3,linear.output=TRUE)
nn_2
par(mfrow=c(1,1))
plot.nn(nn_2)
```

View the neural network structure and the content of the model

```{r five}
ls(nn_2)
nn_2$result.matrix
nn_2$net.result[[1]][1:20]
nn_2$covariate[1:20]
out<-cbind(nn_2$covariate,nn_2$net.result[[1]])
n
dimnames(out)<-list(NULL,c("open","high","low","volume","nn-output"))
head(out)
head(nn_2$generalized.weights[[1]])
```

Generalized weights

```{r six}
par(mfrow=c(2,2))
gwplot(nn_2,selected.covariate="open",min=-50,max=50)
gwplot(nn_2,selected.covariate="high",min=-50,max=50)
gwplot(nn_2,selected.covariate="low",min=-50,max=50)
gwplot(nn_2,selected.covariate="volume",min=-50,max=50)
```

Using the model to predict the close price

```{r seven}
test_$close<-NULL
head(test_)
pr.nn<-compute(nn_2,test_)
ls(pr.nn)
pr.nn$net.result[1:20]
pr.nn_result<-pr.nn$net.result*sd(A_index$close)+mean(A_index$close)
test_.result<-test$close
pr.nn_result[1:20]
```

Plot the prediction

```{r eight}
par(mfrow=c(1,1))
fig_1<-plot(test$close,pr.nn_result,ylab="Model nn_2 predict value",xlab="Real value",ylim=c(2000,2500),col="red",main="Real vs Predicted Neural Network",pch=18,cex=0.7)
abline(0,1,lwd=2)
legend("bottomright",legend="NN",pch=18,col="red",bty="n")
```

Result table for prediction vs real value and MSE

```{r nine}
new_dates<-dates[c(501:623)]
result<-data.frame(new_dates,test$close,pr.nn_result)
head(result)
percent<-(round(pr.nn_result,2)-round(test$close,2))*100/round(test$close,2)
res<-paste("Date:",new_dates,"Predicted:",round(pr.nn_result,2),"Real:",round(test$close,2),"Residuals:",paste(round(percent,2),"%"))
head(res)
MSE.nn<-sum((result$test.close-result$pr.nn_result)^2)/nrow(result)
MSE.nn
```

Plot the trend 

```{r ten}
library(reshape2)
library(ggplot2)
library(ggthemes)
final<-melt(result,id=c("new_dates"))
fig_1<-ggplot(final,aes(x=new_dates,y=value,color=variable))+geom_line()+ggtitle("2014-02~2014-07 Real VS Predict ")+xlab("Month")+ylab("Index")+ylim(2000,2500)
fig_1+theme_tufte()
```

##According to the correlation analysis  and generalized weights analysis that volume has little influence to the model, so build a new model without it.

```{r eleven}
nn.new<-neuralnet(close~open+high+low,data=train_,hidden=3,linear.output=TRUE)
nn.new
nn.new_hidden_2<-neuralnet(close~open+high+low,data=train_,hidden=2,linear.output=TRUE)
nn.new_hidden_2
par(mfrow=c(1,1))
plot.nn(nn.new)
ls(nn.new)
nn.new$result.matrix
```

Using the new model to predict the close price

```{r twelve}
pr.nn.new<-compute(nn.new,test_[,c(1:3)])
ls(pr.nn.new)
pr.nn.new$net.result[1:20]
pr.nn.new_result<-pr.nn.new$net.result*sd(A_index$close)+mean(A_index$close)
par(mfrow=c(1,1))
fig_2<-plot(test$close,pr.nn.new_result,ylab="Model nn_new predict value",xlab="Real value",col="blue",main="Real vs Predicted Neural Network",pch=18,cex=0.7)
abline(0,1,lwd=2)
legend("bottomright",legend="NN",pch=18,col="blue",bty="n")
```

Result table for prediction vs real value and MSE in new model

```{r thirteen}
result2<-data.frame(new_dates,test$close,pr.nn.new_result)
head(result2)
percent2<-(round(pr.nn.new_result,2)-round(test$close,2))*100/round(test$close,2)
res_new<-paste("Date:",new_dates,"Predicted:",round(pr.nn.new_result,2),"Real:",round(test$close,2),"Residuals:",paste(round(percent2,2),"%"))
head(res_new)
MSE.nn_new<-sum((result2$test.close-result2$pr.nn.new_result)^2)/nrow(result2)
MSE.nn_new
```

Plot the trend in new model

```{r}
final_new<-melt(result2,id=c("new_dates"))
library(ggplot2)
fig_2<-ggplot(final_new,aes(x=new_dates,y=value,color=variable))+geom_line()+ggtitle("2014-02~2014-07 Real VS Predict New ")+xlab("Month")+ylab("Index")
fig_2+theme_tufte()
```

##The two RPROP neural network compare

```{r}
print(paste(MSE.nn,MSE.nn_new))
par(mfrow=c(1,1))
fig_3<-plot(test$close,pr.nn.new_result,ylab=" Predict value ",xlab="Real value",col="blue",main="Real vs Predicted Neural Network",pch=18,cex=0.7)
points(test$close,pr.nn_result,col="red",pch=18,cex=0.7)
abline(0,1,lwd=2)
legend("bottomright",legend=c("nn_new","nn_2"),pch=18,col=c("blue","red"))
```

##Compare with BP neural network

```{r}
library(nnet)
nn.net<-nnet(close~open+high+low,data=train_,size=3,linout=T,abstol=0.01)
plot.nn(nn.net)
net.predict<-predict(nn.net,test_[,c(1:3)])
pr.nn.net_result<-net.predict*sd(A_index$close)+mean(A_index$close)
result3<-data.frame(new_dates,test$close,pr.nn.net_result)
MSE.nn_net<-sum((result3$test.close-result3$pr.nn.net_result)^2)/nrow(result3)
result4<-result2
result4$pr.nn.net_result<-pr.nn.net_result
head(result4)
print(paste(MSE.nn_new,MSE.nn_net))
```

```{r}
par(mfrow=c(1,1))
fig_4<-plot(test$close,pr.nn.new_result,ylab=" Predict value ",xlab="Real value",col="green",main="Real vs Predicted Neural Network",pch=18,cex=0.7)
points(test$close,pr.nn.net_result,col="red",pch=18,cex=0.7)
abline(0,1,lwd=2)
legend("bottomright",legend=c("nn_new","nn_net"),pch=18,col=c("green","red"))
```

##Confidence Interval

```{r}
ci_nn_1<-confidence.interval(nn_2,alpha=0.05)
ls(ci_nn_1)
ci_nn_1$lower.ci
ci_nn_1$upper.ci
ci_nn_new<-confidence.interval(nn.new,alpha=0.05)
ci_nn_new$lower.ci
ci_nn_new$upper.ci
```

##Cross Validation

Cross Validation for nn_2

```{r}
set.seed(450)
cv.error_2<-NULL
k2<-10
library(plyr)
pbar<-create_progress_bar('text')
pbar$init(k2)
for(i in 1:k2){
  index<-sample(1:nrow(A_index),round(0.9*nrow(A_index)))
  train_cv<-A_index[index,]
  test_cv<-A_index[-index,]
  train.cv<-scaled[index,]
  test.cv<-scaled[-index,]
  nn.cv_2<-neuralnet(close~open+high+low+volume,data=train.cv,hidden=3,linear.output=T)
  test.cv$close<-NULL
  pr.nn.cv_2<-compute(nn.cv_2,test.cv)
  pr.nn.cv_new_2<-pr.nn.cv_2$net.result*sd(A_index$close)+mean(A_index$close)
  test.cv.r<-test_cv$close
  cv.error_2[i]<-sum((test.cv.r-pr.nn.cv_new_2)^2)/nrow(test.cv)
  pbar$step()
}
cv.error_2
mean(cv.error_2)
```

Boxplot for cv.error_2

```{r}
boxplot(cv.error_2,xlab="MSE CV",col='hotpink',border='red',names='CV error(MSE)',main='CV error(MSE) for nn_2',horizontal=T)
```

Cross validation for nn_new

```{r}
set.seed(450)
cv.error<-NULL
k<-10
library(plyr)
pbar<-create_progress_bar('text')
pbar$init(k)
for(i in 1:k){
  index<-sample(1:nrow(A_index),round(0.9*nrow(A_index)))
  train_cv<-A_index[index,]
  test_cv<-A_index[-index,]
  train.cv<-scaled[index,]
  test.cv<-scaled[-index,]
  nn.cv<-neuralnet(close~open+high+low,data=train.cv,hidden=3,linear.output=T)
  test.cv$close<-NULL
  pr.nn.cv<-compute(nn.cv,test.cv[,1:3])
  pr.nn.cv_new<-pr.nn.cv$net.result*sd(A_index$close)+mean(A_index$close)
  test.cv.r<-test_cv$close
  cv.error[i]<-sum((test.cv.r-pr.nn.cv_new)^2)/nrow(test.cv)
  pbar$step()
}
cv.error
mean(cv.error)
```

Boxplot for cv.error

```{r}
boxplot(cv.error,xlab="MSE CV",col='steelblue',border='blue',names='CV error(MSE)',main='CV error(MSE) for nn_new',horizontal=T)
```

Cross Validation for nn_net

```{r}
set.seed(450)
cv.error_3<-NULL
k3<-10
library(plyr)
pbar<-create_progress_bar('text')
pbar$init(k3)
for(i in 1:k3){
  index<-sample(1:nrow(A_index),round(0.9*nrow(A_index)))
  train_cv<-A_index[index,]
  test_cv<-A_index[-index,]
  train.cv<-scaled[index,]
  test.cv<-scaled[-index,]
  nn.cv_3<-nnet(close~open+high+low,data=train.cv,size=3,linout=T,abstol=0.01)
  test.cv$close<-NULL
  pr.nn.cv_3<-predict(nn.cv_3,test.cv)
  pr.nn.cv_new_3<-pr.nn.cv_3*sd(A_index$close)+mean(A_index$close)
  test.cv.r<-test_cv$close
  cv.error_3[i]<-sum((test.cv.r-pr.nn.cv_new_3)^2)/nrow(test.cv)
  pbar$step()
}
cv.error_3
mean(cv.error_3)
```

Boxplot for cv.error_3

```{r}
boxplot(cv.error_3,xlab="MSE CV",col='mediumturquoise',border='green',names='CV error(MSE)',main='CV error(MSE) for nn_net',horizontal=T)
```

## Predict data from 2014-7~2014-12
```{r}
getwd()
setwd('/Users/zhoudan/Neural Network')
new_data<-data.frame(read.csv("000002.csv",header=T))
head(new_data)
apply(new_data, 2, function(x) sum(is.na(x)))
dates_new<-as.Date(new_data[,1])
new_data$date<-NULL
head(new_data)
nrow(new_data)
train_new<-new_data[c(0:600),]
test_new<-new_data[c(601:726),]
scaled_new<-as.data.frame(scale(new_data))
train_new_<-scaled_new[c(0:600),]
test_new_<-scaled_new[c(601:726),]
head(train_new_)
head(test_new_)
library(neuralnet)
nn.new_data<-neuralnet(close~open+high+low,data=train_new_,hidden=3,linear.output=TRUE)
test_new_$close<-NULL
pr.nn.new_data<-compute(nn.new_data,test_new_)
pr.nn.new_result_data<-pr.nn.new_data$net.result*sd(new_data$close)+mean(new_data$close)
Dates<-dates_new[601:726]
result5<-data.frame(Dates,test_new$close,pr.nn.new_result_data)
library(reshape)
library(ggthemes)
final_new_data<-melt(result5,id=c("Dates"))
library(ggplot2)
fig_5<-ggplot(final_new_data,aes(x=Dates,y=value,color=variable))+geom_line()+ggtitle("2014-07~2014-12 Real VS Predict")+xlab("Month")+ylab("Index")
fig_5+theme_tufte()
```






